PM Component Paper Plots

### 2021-01-30 code/data-viz/plot-results.Rmd
new analysis - configs - clean outputs - plots

```{r}
### load packages
  library(tidyverse)
  library(here)
  library(gridExtra)
```

```{r Load data}
load(here('output','analysis','out-pmc-base.RDa'))
load(here('output','analysis','out-pmc-ses.RDa'))
load(here('output','analysis','out-fac-base.RDa'))
load(here('output','analysis','out-fac-ses.RDa'))
load(here('output','analysis','out-fac-ex-ec-base.RDa'))
load(here('output','analysis','out-fac-ex-ec-ses.RDa'))
load(here('output','analysis','out-pmc-resid.RDa'))
load(here('output','analysis','out-fac-resid.RDa'))
load(here('output','analysis','out-pmc-region.RDa'))
load(here('output','analysis','out-pmc-race.RDa'))
load(here('output','analysis','out-pmc-urbanicity.RDa'))
load(here('output','analysis','out-pmc-sescat.RDa'))
load(here('output','analysis','out-pmc-brfss.RDa'))
load(here('output','analysis','out-pmc-age.RDa'))
load(here('output','analysis','out-pmc-sex.RDa'))
load(here('output','analysis','out-pmc-buffer.RDa'))
load(here('output','analysis','out-pmc-expo.RDa'))
```

@@

plot_cols <- c("#D71A21")

ggplot(data, aes(x = HR, xmin = HR.L, xmax = HR.U, y = Index)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  xlab("") +
  ylab("") +
  geom_segment(aes(x = HR.L, xend = HR.U, y = Index, yend = Index),
              color =plot_cols, size = 0.25, show.legend = F) + 
  geom_point(aes(x = HR, y = Index, shape = as.factor(sig)), 
             color =plot_cols, size = 1.5, show.legend = F) + 
  scale_shape_manual(values = c(16, 1, 16), guide = F) +

facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25, 'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_text(size = 8, face = 'bold', color = 'black'),
  ) +
ggsave(here('output', 'plot','pmc-base.png'), width = 6.5, height = 8.5)
```

@@

plot_cols <- c("#D71A21")

ggplot(data, aes(x = HR, xmin = HR.L, xmax = HR.U, y = Index)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  xlab("") +
  ylab("") +
  geom_segment(aes(x = HR.L, xend = HR.U, y = Index, yend = Index),
              color =plot_cols, size = 0.25, show.legend = F) + 
  geom_point(aes(x = HR, y = Index, shape = as.factor(sig)), 
             color =plot_cols, size = 1.5, show.legend = F) + 
  scale_shape_manual(values = c(16, 1, 16), guide = F) +

facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25, 'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_text(size = 8, face = 'bold', color = 'black'),
  ) +
ggsave(here('output', 'plot','pmc-ses.png'), width = 6.5, height = 8.5)
```

```{r - Factor Base}
data <- out.fac.base

@@

plot_cols <- c("#D71A21")

ggplot(data, aes(x = HR, xmin = HR.L, xmax = HR.U, y = Index)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  geom_vline(xintercept = 1.2, linetype = 2, alpha = 0) +
  xlab("") +
  ylab("") +
  #scale_x_continuous(breaks=c(1, 1.1, 1.2)) + 
  geom_segment(aes(x = HR.L, xend = HR.U, y = Index, yend = Index),
               color =plot_cols, size = 0.25, show.legend = F) + 
  geom_point(aes(x = HR, y = Index, shape = as.factor(sig)), 
             color =plot_cols, size = 1.5, show.legend = F) + 
  scale_shape_manual(values = c(16, 1, 16), guide = F) +

facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_text(size = 8, face = 'bold', color = 'black'),
  ) +
ggsave(here('output', 'plot','fac-base-ec.png'), width = 6.5, height = 8.5)
```

```{r - Factor SES-Adj}
data <- out.fac.ses

@@

plot_cols <- c("#D71A21")

ggplot(data, aes(x = HR, xmin = HR.L, xmax = HR.U, y = Index)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  geom_vline(xintercept = 1.2, linetype = 2, alpha = 0) +
  xlab("") +
  ylab("") +
  #scale_x_continuous(breaks=c(1, 1.1, 1.2)) + 
  geom_segment(aes(x = HR.L, xend = HR.U, y = Index, yend = Index),
               color =plot_cols, size = 0.25, show.legend = F) + 
  geom_point(aes(x = HR, y = Index, shape = as.factor(sig)), 
             color =plot_cols, size = 1.5, show.legend = F) + 
  scale_shape_manual(values = c(16, 1, 16), guide = F) +

facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_text(size = 8, face = 'bold', color = 'black'),
  ) +
ggsave(here('output', 'plot','fac-ses-ec.png'), width = 6.5, height = 8.5)
```

```{r - Factor Ex. EC Base}
data <- out.fac.ex.ec.base

@@

plot_cols <- c("#D71A21")

ggplot(data, aes(x = HR, xmin = HR.L, xmax = HR.U, y = Index)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  geom_vline(xintercept = 1.2, linetype = 2, alpha = 0) +
  xlab("") +
  ylab("") +
  #scale_x_continuous(breaks=c(1, 1.1, 1.2)) + 
  geom_segment(aes(x = HR.L, xend = HR.U, y = Index, yend = Index),
               color =plot_cols, size = 0.25, show.legend = F) + 
  geom_point(aes(x = HR, y = Index, shape = as.factor(sig)), 
             color =plot_cols, size = 1.5, show.legend = F) + 
  scale_shape_manual(values = c(16, 1, 16), guide = F) +

facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_text(size = 8, face = 'bold', color = 'black'),
  ) +
ggsave(here('output', 'plot','fac-base.png'), width = 6.5, height = 8.5)
```

```{r - Factor EX. EC SES-Adj}
data <- out.fac.ex.ec.ses

@@

plot_cols <- c("#D71A21")

ggplot(data, aes(x = HR, xmin = HR.L, xmax = HR.U, y = Index)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  geom_vline(xintercept = 1.2, linetype = 2, alpha = 0) +
  xlab("") +
  ylab("") +
  #scale_x_continuous(breaks=c(1, 1.1, 1.2)) + 
  geom_segment(aes(x = HR.L, xend = HR.U, y = Index, yend = Index),
               color =plot_cols, size = 0.25, show.legend = F) + 
  geom_point(aes(x = HR, y = Index, shape = as.factor(sig)), 
             color =plot_cols, size = 1.5, show.legend = F) + 
  scale_shape_manual(values = c(16, 1, 16), guide = F) +

facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_text(size = 8, face = 'bold', color = 'black'),
  ) +
ggsave(here('output', 'plot','fac-ses.png'), width = 6.5, height = 8.5)
```

@@

plot_cols <- c("#D71A21")

ggplot(data, aes(x = HR, xmin = HR.L, xmax = HR.U, y = Index)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  xlab("") +
  ylab("") +
  geom_segment(aes(x = HR.L, xend = HR.U, y = Index, yend = Index),
               color =plot_cols, size = 0.25, show.legend = F) + 
  geom_point(aes(x = HR, y = Index, shape = as.factor(sig)), 
             color =plot_cols, size = 1.5, show.legend = F) +
  scale_shape_manual(values = c(16, 1, 16), guide = F) +

facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_text(size = 8, face = 'bold', color = 'black'),
  ) +
ggsave(here('output', 'plot','pmc-resid.png'), width = 6.5, height = 8.5)
```

```{r - Components PM Residual - Region}
data <- read_excel('Comp_PMResi_Region.xlsx')

cmp <- c("PM2.5",  "-Si", "-Ca", "-Pb", "-Zn",
         "-Se", "-SO4", "-Ni", "-V", "-NO3", "-OC"
         )
cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", 
         "Respiratory", "Pneumonia",
         "Cancer","Lung Cancer") # "CHF", "COPD",

data <- data %>% 
  filter(Index %in% cmp,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp),
         Tag = as.factor(Tag)
         )

p <- grid.arrange(
ggplot(data = filter(data, Cause %in% c ("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF")),
       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  xlab("") +
  ylab("") +
  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
                size = 0.25, show.legend = F) + 
  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
             size = 1.5, show.legend = F) + 
  scale_shape_manual(values = c(16, 1, 16), guide = F) +
  scale_color_manual(
    labels = plot_labs,
    values = plot_cols) +

facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
               shrink = T, space = 'fixed') +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25,0,0.25,0),'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
        strip.text.y.left = element_text(angle = 0),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = 'bottom',
        legend.title = element_blank(),
        legend.text = element_text(size = 10, face = "bold"),
        legend.key.width = unit(0.25, units = 'in')) +
  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),

ggplot(data = filter(data, Cause %in% c ("Respiratory", "COPD", "Pneumonia", "Cancer", "Lung Cancer")),
       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  xlab("") +
  ylab("") +
  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
                size = 0.25, show.legend = F) + 
  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
             size = 1.5, show.legend = F) + 
  scale_shape_manual(values = c(16, 1, 16), guide = F) +
  scale_color_manual(
    labels = plot_labs, 
    values = plot_cols) +

facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
               shrink = T, space = 'fixed') +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25,0,0.25,0),'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.text.y = element_text(size = 10,face = "bold", color = "black", angle = 180),
        strip.text.y.left = element_text(angle = 0),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = 'bottom',
        legend.title = element_blank(),
        legend.text = element_text(size = 10, face = "bold"),
        legend.key.width = unit(0.25, units = 'in')) +
  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
nrow = 2)

ggsave("CMP_PMResi_Region_1113.jpeg", p, width = 9.5, height = 12)
```

@@

plot_cols <- c("#D71A21")

ggplot(data, aes(x = HR, xmin = HR.L, xmax = HR.U, y = Index)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  xlab("") +
  ylab("") +
  geom_segment(aes(x = HR.L, xend = HR.U, y = Index, yend = Index),
              color =plot_cols, size = 0.25, show.legend = F) + 
  geom_point(aes(x = HR, y = Index, shape = as.factor(sig)), 
             color =plot_cols, size = 1.5, show.legend = F) + 
  scale_shape_manual(values = c(16, 1, 16), guide = F) +

facet_wrap( ~ Cause, nrow = 2, scales = "fixed") +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_text(size = 8, face = 'bold', color = 'black'),
  ) +
ggsave(here('output', 'plot','fac-resid.png'), width = 6.5, height = 8.5)
```

>>>>

```{r}
### load packages
  library(tidyverse)
  library(here)
  library(gridExtra)
  library(ggthemes)
```

```{r set theme}
ggtheme1 <- theme_bw() + 
  theme(panel.spacing.x = unit(0.25, 'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.background = element_rect(fill = "#B9CFED"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_text(size = 8, face = 'bold', color = 'black'),
  )
```

```{r}
ggtheme2 <- theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25,0,0.25,0,0.25,0),'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
        strip.text.y.left = element_text(angle = 0),
        strip.background = element_rect(fill = "#B9CFED"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = 'bottom',
        legend.title = element_blank(),
        legend.text = element_text(size = 10, face = "bold"),
        legend.key.width = unit(0.25, units = 'in'))
```

```{r Load data}
load(here('output','analysis','out-pmc-base.RDa'))
load(here('output','analysis','out-pmc-ses.RDa'))
load(here('output','analysis','out-fac-base.RDa'))
load(here('output','analysis','out-fac-ses.RDa'))
load(here('output','analysis','out-fac-base-ec.RDa'))
load(here('output','analysis','out-fac-ses-ec.RDa'))
load(here('output','analysis','out-pmc-resid.RDa'))
load(here('output','analysis','out-fac-resid.RDa'))
load(here('output','analysis','out-pmc-age.RDa'))
load(here('output','analysis','out-fac-age.RDa'))
load(here('output','analysis','out-pmc-sex.RDa'))
load(here('output','analysis','out-fac-sex.RDa'))
load(here('output','analysis','out-pmc-race.RDa'))
load(here('output','analysis','out-fac-race.RDa'))
load(here('output','analysis','out-pmc-urbanicity.RDa'))
load(here('output','analysis','out-pmc-sescat.RDa'))
load(here('output','analysis','out-pmc-region.RDa'))
load(here('output','analysis','out-pmc-brfss.RDa'))
load(here('output','analysis','out-pmc-buffer.RDa'))
load(here('output','analysis','out-pmc-expo.RDa'))
```

```{r color code}
#https://www.schemecolor.com/british-airways-website.php
```

@@

plot_cols <- c("#EB2226")

ggplot(data, aes(x = HR, xmin = HR.L, xmax = HR.U, y = Index)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  labs(x = "", y = "") +
  geom_segment(aes(x = HR.L, xend = HR.U, y = Index, yend = Index),
              color =plot_cols, size = 0.25, show.legend = F) + 
  geom_point(aes(x = HR, y = Index, shape = as.factor(sig)), 
             color =plot_cols, size = 1.5, show.legend = F) + 
  scale_shape_manual(values = c(16, 1, 16), guide = F) +
facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
  ggtheme1 +
ggsave(here('output','plot','pmc-base.png'), width = 6.5, height = 6.5)
```

@@

plot_cols <- c("#EB2226")

ggplot(data, aes(x = HR, xmin = HR.L, xmax = HR.U, y = Index)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  labs(x = "", y = "") +
  geom_segment(aes(x = HR.L, xend = HR.U, y = Index, yend = Index),
              color =plot_cols, size = 0.25, show.legend = F) + 
  geom_point(aes(x = HR, y = Index, shape = as.factor(sig)), 
             color =plot_cols, size = 1.5, show.legend = F) + 
  scale_shape_manual(values = c(16, 1, 16), guide = F) +
facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
  ggtheme1 +
ggsave(here('output','plot','pmc-ses.png'), width = 6.5, height = 6.5)
```

```{r - Factor Base Inc EC}
data <- out.fac.base.ec

@@

plot_cols <- c("#EB2226")

ggplot(data, aes(x = HR, xmin = HR.L, xmax = HR.U, y = Index)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  labs(x = "", y = "") +
  geom_segment(aes(x = HR.L, xend = HR.U, y = Index, yend = Index),
               color =plot_cols, size = 0.25, show.legend = F) + 
  geom_point(aes(x = HR, y = Index, shape = as.factor(sig)), 
             color =plot_cols, size = 1.5, show.legend = F) + 
  scale_shape_manual(values = c(16, 1, 16), guide = F) +
facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
  ggtheme1 +
ggsave(here('output','plot','fac-base-ec.png'), width = 6.5, height = 6.5)
```

```{r - Factor SES-Adj Inc EC}
data <- out.fac.ses.ec

@@

plot_cols <- c("#EB2226")

ggplot(data, aes(x = HR, xmin = HR.L, xmax = HR.U, y = Index)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  labs(x = "", y = "") +
  geom_segment(aes(x = HR.L, xend = HR.U, y = Index, yend = Index),
               color =plot_cols, size = 0.25, show.legend = F) + 
  geom_point(aes(x = HR, y = Index, shape = as.factor(sig)), 
             color =plot_cols, size = 1.5, show.legend = F) + 
  scale_shape_manual(values = c(16, 1, 16), guide = F) +
facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
  ggtheme1 +
ggsave(here('output','plot','fac-ses-ec.png'), width = 6.5, height = 6.5)
```

```{r - Factor Ex. EC Base}
data <- out.fac.base

@@

plot_cols <- c("#EB2226")

ggplot(data, aes(x = HR, xmin = HR.L, xmax = HR.U, y = Index)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  labs(x = "", y = "") +
  geom_segment(aes(x = HR.L, xend = HR.U, y = Index, yend = Index),
               color =plot_cols, size = 0.25, show.legend = F) + 
  geom_point(aes(x = HR, y = Index, shape = as.factor(sig)), 
             color =plot_cols, size = 1.5, show.legend = F) + 
  scale_shape_manual(values = c(16, 1, 16), guide = F) +
facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
  ggtheme1 +
ggsave(here('output','plot','fac-base.png'), width = 6.5, height = 6.5)
```

```{r - Factor EX. EC SES-Adj}
data <- out.fac.ses

@@

plot_cols <- c("#EB2226")

ggplot(data, aes(x = HR, xmin = HR.L, xmax = HR.U, y = Index)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  labs(x = "", y = "") +
  geom_segment(aes(x = HR.L, xend = HR.U, y = Index, yend = Index),
               color =plot_cols, size = 0.25, show.legend = F) + 
  geom_point(aes(x = HR, y = Index, shape = as.factor(sig)), 
             color =plot_cols, size = 1.5, show.legend = F) + 
  scale_shape_manual(values = c(16, 1, 16), guide = F) +
facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
  ggtheme1 +
ggsave(here('output','plot','fac-ses.png'), width = 6.5, height = 6.5)
```

@@

plot_cols <- c("#EB2226")

ggplot(data, aes(x = HR, xmin = HR.L, xmax = HR.U, y = Index)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  labs(x = "", y = "") +
  geom_segment(aes(x = HR.L, xend = HR.U, y = Index, yend = Index),
               color =plot_cols, size = 0.25, show.legend = F) + 
  geom_point(aes(x = HR, y = Index, shape = as.factor(sig)), 
             color =plot_cols, size = 1.5, show.legend = F) +
  scale_shape_manual(values = c(16, 1, 16), guide = F) +
facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
  ggtheme1 +
ggsave(here('output','plot','pmc-resid.png'), width = 6.5, height = 6.5)
```

@@

plot_cols <- c("#EB2226")

ggplot(data, aes(x = HR, xmin = HR.L, xmax = HR.U, y = Index)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  labs(x = "", y = "") +
  geom_segment(aes(x = HR.L, xend = HR.U, y = Index, yend = Index),
              color =plot_cols, size = 0.25, show.legend = F) + 
  geom_point(aes(x = HR, y = Index, shape = as.factor(sig)), 
             color =plot_cols, size = 1.5, show.legend = F) + 
  scale_shape_manual(values = c(16, 1, 16), guide = F) +
facet_wrap( ~ Cause, nrow = 2, scales = "fixed") +
  ggtheme1 +
ggsave(here('output', 'plot','fac-resid.png'), width = 6.5, height = 6.5)
```

plot_labs <- c("> 75 years", "<= 75 years")
plot_cols <- c("#EB2226", "#075AAA")

p <- grid.arrange(
ggplot(data = filter(data, Cause %in% c ("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF")),
       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  labs(x = "", y = "") +
  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
                size = 0.25, show.legend = F) + 
  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
             size = 1.5, show.legend = F) + 
  scale_shape_manual(values = c(16, 1, 16), guide = F) +
  scale_color_manual(
    labels = plot_labs, 
    values = plot_cols) +

facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
               shrink = T, space = 'fixed') +
  ggtheme2 +
  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),

ggplot(data = filter(data, Cause %in% c ("Respiratory", "COPD", "Pneumonia", "Cancer", "Lung Cancer")),
       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  labs(x = "", y = "") +
  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
                size = 0.25, show.legend = T) + 
  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
             size = 1.5, show.legend = T) + 
  scale_shape_manual(values = c(16, 1, 16), guide = F) +
  scale_color_manual(
    labels = plot_labs, 
    values = plot_cols) +
facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
               shrink = T, space = 'fixed') +
  ggtheme2 +
  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
nrow = 2)

ggsave(here('output', 'plot','pmc-age.png'),p, width = 6.5, height = 6.5)
```

plot_labs <- c("Male", "Female")
plot_cols <- c("#EB2226", "#075AAA")

p <- grid.arrange(
ggplot(data = filter(data, Cause %in% c ("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF")),
       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  labs(x = "", y = "") +
  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
                size = 0.25, show.legend = F) + 
  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
             size = 1.5, show.legend = F) + 
  scale_shape_manual(values = c(16, 1, 16), guide = F) +
  scale_color_manual(
    labels = plot_labs, 
    values = plot_cols) +
facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
               shrink = T, space = 'fixed') +
  ggtheme2 +
  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),

ggplot(data = filter(data, Cause %in% c ("Respiratory", "COPD", "Pneumonia", "Cancer", "Lung Cancer")),
       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  labs(x = "", y = "") +
  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
                size = 0.25, show.legend = T) + 
  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
             size = 1.5, show.legend = T) + 
  scale_shape_manual(values = c(16, 1, 16), guide = F) +
  scale_color_manual(
    labels = plot_labs, 
    values = plot_cols) +
facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
               shrink = T, space = 'fixed') +
  ggtheme2 +
  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
nrow = 2)

ggsave(here('output', 'plot','pmc-sex.png'),p, width = 6.5, height = 6.5)
```

plot_labs <- c("White", "Hispanic", "Black", "Asian")
plot_cols <- c("#EB2226", "orange", "#075AAA", "seagreen")

p <- grid.arrange(
ggplot(data = filter(data, Cause %in% c ("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF")),
       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  labs(x = "", y = "") +
  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
                size = 0.25, show.legend = F) + 
  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
             size = 1.5, show.legend = F) + 
  scale_shape_manual(values = c(16, 1, 16), guide = F) +
  scale_color_manual(
    labels = plot_labs, 
    values = plot_cols) +
facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
               shrink = T, space = 'fixed') +
  ggtheme2 +
  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),

ggplot(data = filter(data, Cause %in% c ("Respiratory", "COPD", "Pneumonia", "Cancer", "Lung Cancer")),
       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  labs(x = "", y = "") +
  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
                size = 0.25, show.legend = T) + 
  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
             size = 1.5, show.legend = T) + 
  scale_shape_manual(values = c(16, 1, 16), guide = F) +
  scale_color_manual(
    labels = plot_labs, 
    values = plot_cols) +
facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
               shrink = T, space = 'fixed') +
  ggtheme2 +
  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
nrow = 2)

ggsave(here('output', 'plot','pmc-race.png'),p, width = 6.5, height = 6.5)
```

plot_labs <- c("Non-urban", "Urban")
plot_cols <- c("#EB2226", "#075AAA")

p <- grid.arrange(
ggplot(data = filter(data, Cause %in% c ("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF")),
       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  labs(x = "", y = "") +
  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
                size = 0.25, show.legend = F) + 
  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
             size = 1.5, show.legend = F) + 
  scale_shape_manual(values = c(16, 1, 16), guide = F) +
  scale_color_manual(
    labels = plot_labs, 
    values = plot_cols) +
facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
               shrink = T, space = 'fixed') +
  ggtheme2 +
  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),

ggplot(data = filter(data, Cause %in% c ("Respiratory", "COPD", "Pneumonia", "Cancer", "Lung Cancer")),
       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  labs(x = "", y = "") +
  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
                size = 0.25, show.legend = T) + 
  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
             size = 1.5, show.legend = T) + 
  scale_shape_manual(values = c(16, 1, 16), guide = F) +
  scale_color_manual(
    labels = plot_labs, 
    values = plot_cols) +
facet_grid(Index ~ Cause,  scales = "fixed", switch = 'y',
               shrink = T, space = 'fixed') +
  ggtheme2 +
  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
nrow = 2)

ggsave(here('output', 'plot','pmc-urbanicity.png'),p, width = 6.5, height = 6.5)
```

plot_labs <- c("High", "Middle", "Low")
plot_cols <-  c("seagreen", "#075AAA", "#EB2226")

p <- grid.arrange(
ggplot(data = filter(data, Cause %in% c ("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF")),
       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  labs(x = "", y = "") +
  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
                size = 0.25, show.legend = F) + 
  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
             size = 1.5, show.legend = F) + 
  scale_shape_manual(values = c(16, 1, 16), guide = F) +
  scale_color_manual(
    labels = plot_labs, 
    values = plot_cols) +
facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
               shrink = T, space = 'fixed') +
  ggtheme2 +
  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
